Adversarial Training of Invariant Features for Speech Recognition

### 2017-03-21 interspeech/paper.tex
Some cosmetic changes

    Several model and feature based adaptation methods such as Maximum 
    Likelihood Linear Regression (MLLR),  feature-based MLLR and 
    iVectors~\citep{saon2013speaker} have been proposed to handle speaker 
    variability; and Noise Adaptive Training \citep[NAT;][]{kalinli2010noise}
    and Vector Taylor Series \citep[VTS;][]{un1998speech} to handle 
    environment variability.
    % The end-to-end part has become sort of irrelevant given that the
    % experiments are actually with hybrid systems and this version of the paper will not
    % have to be sold as being end-to-end anymore.
    With the increasing success of Deep Neural 
    Network~(DNN) acoustic models for ASR investigated 
    in~\citep{hinton2012deep,seide2011conversational,sainath2011making}, 
    and in more recent works~\citep{miao2015eesen,sainath2015learning} 
    complicated structure of acoustic conditions is modeled within a single network.
    This allows us to take 
    advantage of the network's ability to learn highly non-linear feature 
    transformations, with greater flexibility in constructing training 
    objective functions that promote learning of noise invariant 
    representations.
    % Phil: The part below should include speaker invariance and mention the WSJ task
    The main idea of this work is to force the acoustic model 
    to learn a representation which is invariant to noise conditions, instead of 
    explicitly using noise robust acoustic features 
    (Section~\ref{sec:invariant-speech}). This type of noise-invariant 
    training requires noise-condition labels during training only. It is 
    related to the idea of generative adversarial networks (GAN) and the 
    gradient reverse method proposed by~\cite{goodfellow2014generative} 
    and~\cite{ganin2014unsupervised} respectively 
    (Section~\ref{sec:background}). Then we discuss previous work in 
    Section~\ref{sec:relatedwork}. 
    We present results on the Aurora-4 speech 
    recognition task in Section~\ref{sec:experiments} and summarize 
    our findings in Section~\ref{sec:discussion}.

@@

    Prior work by~\cite{ganin2014unsupervised} proposed a method for training a network 
    which can be adapted to new domains. The training data consists of the images
    labeled with classes of interest and separate domain (image background) labels. 
    The network has a $Y$-like structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this 
    representation $h$ is input to two separate networks: a domain classifier network (D) and 
    a target classifier network (R). The goal of training is to learn a hidden 
    representation that is invariant to the domain labels and still performs well on 
    the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time. Similar to the GAN 
    objective, which forces the generation distribution be close to the data distribution,
    the \emph{gradient reverse method} makes domain specific distributions similar to each other.

@@

\section{Related Work}
\label{sec:relatedwork}
    %TODO
    Neural networks display some robustness towards different recording
    conditions and speaker by themselves and the effectiveness of representations
    produced by a neural network for internal 
    noise reduction is discussed by~\cite{yu2013feature}. This work sets a 
    baseline for experiments on the Aurora-4 dataset.

@@

    Many neural network speaker adaptation methods are based on
    i-vectors. The most common way to exploit i-vectors is by providing them as additional
    inputs \cite{senior2014improving,saon2013speaker}. This means that i-vectors also need to
    be available during testing and this may not always be practical.

    In the specific case of noise robustness, one can use speech enhancement to
    obtain more robust features and neural networks have been used for this for
    decades \cite{knecht1995neural}. A further step in this direction is to train
    systems to recognize speech and perform speech enhancement jointly \cite{narayanan2014joint}. 
    We argue that speech enhancement is a more difficult task to learn than
    invariance to certain noise conditions and more likely to suffer from
    overfitting when the amount of available noisy data is limited.

    Another adaptation strategy is to retrain the model parameters using a very small
    number of utterances from the new domain while making sure that the model
    doesn't stray too far away from the parameter values that were obtained from
    the train data \cite{yu2013kl}.
    The adaptation to new domains can also be kept under control by limiting
    the number of parameters which are adapted to the new data or by limiting the
    adaptation to a rescaling of the hidden unit activations
    \cite{swietojanski2014learning}.
    The most important difference between these approaches and our work is that
    we don't adapt the model parameters at all after training. In many
    situations this may not be possible and retraining of models may require more
    from the hardware on which the speech recognition system is implemented.

    Recently, in a work by~\cite{yusuke2016adversarial} a multi-layer sigmoidal network was trained 
    in an adversarial fashion on an in-house transcription task corrupted by noise.
    This work is very similar to our approach but we evaluate our methods on
    more challenging benchmark while investigating different numbers of noise
    conditions. Our work also differs due to the use of more modern rectifier
    activation based classification networks.
    Finally, in other very recent work, \cite{saon2017english} a form of adversarial training with a network
    that predicts an i-vector using the mean square error loss was used.

>>>>

    Several model and feature based adaptation methods such as Maximum 
    Likelihood Linear Regression (MLLR),  feature-based MLLR and 
    i-vectors~\citep{saon2013speaker} have been proposed to handle speaker 
    variability; and Noise Adaptive Training \citep[NAT;][]{kalinli2010noise}
    and Vector Taylor Series \citep[VTS;][]{un1998speech} to handle 
    environment variability.
    % The end-to-end part has become sort of irrelevant given that the
    % experiments are actually with hybrid systems and this version of the paper will not
    % have to be sold as being end-to-end anymore.
    With the increasing success of Deep Neural 
    Network~(DNN) acoustic models for ASR investigated 
    in~\citep{hinton2012deep,seide2011conversational,sainath2011making}, 
    and in more recent works~\citep{miao2015eesen,sainath2015learning} 
    complicated structure of acoustic conditions is modeled within a single network.
    This allows us to take 
    advantage of the network's ability to learn highly non-linear feature 
    transformations, with greater flexibility in constructing training 
    objective functions that promote learning of noise invariant 
    representations.
    % Phil: The part below should include speaker invariance and mention the WSJ task
    The main idea of this work is to force the acoustic model 
    to learn a representation which is invariant to noise conditions, instead of 
    explicitly using noise robust acoustic features 
    (Section~\ref{sec:invariant-speech}). This type of noise-invariant 
    training requires noise-condition labels during training only. It is 
    related to the idea of generative adversarial networks (GAN) and the 
    gradient reverse method proposed by~\cite{goodfellow2014generative} 
    and~\cite{ganin2014unsupervised} respectively 
    (Section~\ref{sec:background}). Then we discuss previous work in 
    Section~\ref{sec:relatedwork}. 
    We present results on the Aurora-4 speech 
    recognition task in Section~\ref{sec:experiments} and summarize 
    our findings in Section~\ref{sec:discussion}.

@@

    % dima: I want to add something like this:
    %Another point of view on the GAN training is that the generator is matching
    %the distribution of the data with the distribution of the generator using
    %a discriminator to provide the training signal. This approach can be generalized
    %on any distributions to be matched.
    Prior work by~\cite{ganin2014unsupervised} proposed a method for training a network 
    which can be adapted to new domains. The training data consists of the images
    labeled with classes of interest and separate domain (image background) labels. 
    The network has a $Y$-like structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this 
    representation $h$ is input to two separate networks: a domain classifier network (D) and 
    a target classifier network (R). The goal of training is to learn a hidden 
    representation that is invariant to the domain labels and still performs well on 
    the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time. Similar to the GAN 
    objective, which forces the generation distribution be close to the data distribution,
    the \emph{gradient reverse method} makes domain specific distributions similar to each other.

@@

\section{Related Work}
\label{sec:relatedwork}
    Neural networks display some robustness towards different recording
    conditions and speaker by themselves and the effectiveness of representations
    produced by a neural network for internal 
    noise reduction is discussed by~\cite{yu2013feature}. This work sets a 
    baseline for experiments on the Aurora-4 dataset.

@@

    Many neural network speaker adaptation methods are based on
    i-vectors. The most common way to exploit i-vectors is by providing them as additional
    inputs~\citep{senior2014improving,saon2013speaker}. This means that i-vectors also need to
    be available during testing and this may not always be practical.

    In the specific case of noise robustness, one can use speech enhancement to
    obtain more robust features and neural networks have been used for this for
    decades~\citep{knecht1995neural}. A further step in this direction is to train
    systems to recognize speech and perform speech enhancement jointly~\citep{narayanan2014joint}. 
    We argue that speech enhancement is a more difficult task to learn than
    invariance to certain noise conditions and more likely to suffer from
    overfitting when the amount of available noisy data is limited.

    Another adaptation strategy is to retrain the model parameters using a very small
    number of utterances from the new domain while making sure that the model
    doesn't stray too far away from the parameter values that were obtained from
    the train data~\citep{yu2013kl}.
    The adaptation to new domains can also be kept under control by limiting
    the number of parameters which are adapted to the new data or by limiting the
    adaptation to a rescaling of the hidden unit activations~\citep{swietojanski2014learning}.
    The most important difference between these approaches and our work is that
    we don't adapt the model parameters at all after training. In many
    situations this may not be possible and retraining of models may require more
    from the hardware on which the speech recognition system is implemented.

    Recently, in a work by~\cite{yusuke2016adversarial} a multi-layer sigmoidal network was trained 
    in an adversarial fashion on an in-house transcription task corrupted by noise.
    This work is very similar to our approach but we evaluate our methods on
    more challenging benchmark while investigating different numbers of noise
    conditions. Our work also differs due to the use of more modern rectifier
    activation based classification networks.
    Finally, in other very recent work~\citep{saon2017english} a form of adversarial training with a network
    that predicts an i-vector using the mean square error loss was used.
